Cryptanalysis of SBC based post-quantum signature scheme \\\textit{Graduation internship report}

### 2025-06-28 rapport.tex
minor changes

\title{Cryptanalysis of SBC based post-quantum signature scheme}

@@

	\section{Introduction}
		Since the emergence of quantum computing in the late 1990s, several breakthroughs have been achieved in the field of quantum algorithms. Some of these advancements have found applications in areas such as medicine and physics, while others have demonstrated the ability to break cryptographic problems that are currently assumed to be hard for classical computers, such as RSA and ECDH.

@@

>>>>

\title{Cryptanalysis of SBC based post-quantum signature scheme \\\textit{Graduation internship report}}

@@

	\section{Introduction}
		Since the emergence of quantum computing in the late 1990s, several breakthroughs have been achieved in the field of quantum algorithms. Some of these advancements have found applications in areas such as medicine and physics, while others have demonstrated the ability to break cryptographic problems that are currently assumed to be hard for classical computers, such as RSA \cite{RSA78} and ECDH.

@@

		We can notice that the output of algorithm \ref{alg:reduc} is polynomials of degree $q$. Here $q$ is always $n_x + 1$ or $n_y + 1$. We deduce that the only non trivial syzygies are of degree $n_x + 1$ or $n_y + 1$. \textbf{c'est pas $n_x + 2$ ou $n_y + 2$ du coup ?}
